% Chapter Template

\chapter{Phase 3 - Building the Interfaces} % Main chapter title

\label{Chapter6} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
The goal for phase 3 is to develop the actual test, beta-test, and deploy it can be accessed and used globally by people all over the world. To be able to do this several diffrent technologies had to be used
\section{Method}
To be able to perform the test on users all over the world without actually having to be there a web based test had to be constructed. The test was made using several different technologies and hosted on aws. 

Several things had to be taken into consideration such as: slower network in china, possibility of web connection getting interrupted, measuring correct behaviours, making sure a completable devices was used for the test (mobile device would not at all test the same thing).


\subsection{Front-End}
based on react boilerplate. Main technologies include(react, redux, sagas, javascript)

Started building the frontend skeleton

then built redux saga

then added language


\subsection{API}

\subsection{Hosting AWS}
To host this app on AWS we used the feature called "Elastic Beanstalk" also called eb. Eb allowed us to easily launch a application that automatically set up a EC2 instance, auto scaling, load-balancing, RDS. We selected to set up the service in Seoul. This to decrease the loading time for China as much as possible. Since Seoul have a very good network connection to the rest of the world as well the loading time is not to much decreased by that in Europe or the US.

\subsection{Database}

\subsection{How the interface works}
pics lots of pics!

\section{Results}

Nunc posuere quam at lectus tristique eu ultrices augue venenatis. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Aliquam erat volutpat. Vivamus sodales tortor eget quam adipiscing in vulputate ante ullamcorper. Sed eros ante, lacinia et sollicitudin et, aliquam sit amet augue. In hac habitasse platea dictumst.

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------

\section{Discussion}

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{Conclusion}
