% Chapter Template

\chapter{Methodology} % Main chapter title

\label{Working_process} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
This chapter aims to present the methodology and layout used in this report to answer the project questions defined in the introduction of this report. Explanation for the layout will be described to clarify the reasoning behind the structure of this paper.


\section{Structure}
This project followed a waterfall based approach where each smaller element in the process was done iteratively. The waterfall based approach suited this project since each step had to be completely finished before moving on to the next part. Each one of these steps, on the other hand, followed a more iterative agile process. One example is the development part of the project, this part could not start until the high-fi was done and tested and the analysis/launch could not be done since the test had to be the same for each user. If any content update was done to the test after launching it all previous results would be invalid. The development process itself was done iteratively, on the other hand, a first alpha version of the test was created and then tested on one or two users (these results were not used in the finished analysis). Then based on user feedback and bugs found the test was improved and then tested again until a satisfied product could be launched.

(figure her with phase 1 to phase 5)

The phases that can be seen in the figure (fig....) represent the different steps of the work process. Each new phase was dependent on the results of the last phase and at the end of each phase what was needed to be done and used in the next phase was decided. Since each phase can be seen as a smaller project they are all divided into a separate chapter in this thesis. Each chapter explains the method used during that phase, what results where found. The validity and relevance of the results are discussed. Lastly, the conclusion explains what was changed were implemented and why. Also what information that was selected for the next phase and how that influences it is explained. 
\\\\
Following the Phase chapters the results of the test are shown in the "Results" chapter, this includes numbers, graphs and calculations done. These results are then discussed in the following chapter "Discussion". We will then try to answer the goal questions stated at the start of this report (ref to that) in the "Conclusion" chapter. What limitations exist for this conclusion and future research necessary will also be discussed in this chapter. 
